Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-13 main.tex
:pencil: Update primary and backscatter rates

\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}

@@

	\begin{section}{The Multi-Tag Case}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems. In the primary downlink system, the AP transmits information to the single-antenna user. In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader. Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging. One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

@@

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
			% It can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
			For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

@@

			Consider the Maximum-Likelihood (ML) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			and the corresponding decision rule is
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{ML}},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is
			\begin{equation}
				T_{i,{i'}}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
				\label{eq:detection_threshold}
			\end{equation}

@@

			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, with CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-rate}
			Before investigating the sum-rate of the tags, we introduce some prerequisites of information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, i.e., $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
				\label{eq:information_function}
			\end{equation}
			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is written as
			\begin{equation}
				I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
				\label{eq:marginal_information_function}
			\end{equation}
			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{equation}
				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
				\label{eq:mutual_information}
			\end{equation}

			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$. Therefore, the mutual information of the tags can be explicitly written as
			\begin{equation}
				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.
				\label{eq:backscatter_sum_rate}
			\end{equation}

			% we can explicitly write the mutual information as

			% obtain the backscatter sum-rate by maximizing the mutual information over the tag input distributions as
			% \begin{equation}
			% 	R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
			% 	\label{eq:backscatter_sum_rate}
			% \end{equation}
		\end{subsection}

		\begin{subsection}{Primary ergodic rate}
			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}. For primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. As such, the ergodic primary mutual information can be expressed as
			\begin{align}
				I_{\mathrm{P}}
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
				\label{eq:primary_ergodic_rate}
			\end{align}
			which is also a function of the tag input distribution $P(c_{\mathcal{K}})$.
		\end{subsection}
	\end{section}

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary ergodic-secondary sum rate region}
			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision region, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
			\begin{maxi!}
				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{I \triangleq \rho I^{\mathrm{P}} + (1 - \rho) I^{\mathrm{B}}}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
			\end{maxi!}
			where $\rho \in [0,1]$ denotes the priority of the primary link. As problem \eqref{op:rate_region} is not jointly convex over $P(c_{\mathcal{K}})$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
		\end{subsection}

		\begin{subsection}{Input distribution}
			Once the decision boundaries $\mathcal{T}$ and the precoder $\boldsymbol{w}$ are determined, obtain the equivalent discrete memoryless MAC by \eqref{eq:mac}. The input distribution optimization subproblem is
			\begin{maxi!}
				{\scriptstyle{P(c_{\mathcal{K}})}}{I}{\label{op:input_distribution}}{\label{ob:weighted_sum_rate_input_distribution}}
				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability_input_distribution}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability_input_distribution}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
			\end{maxi!}

			Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity. The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary MAC (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions. Also, the capacity of an arbitrary MAC is achieved by an elementary MAC included within.}
			% We restrict the discussion of this paper to elementary MACs.

>>>>

\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}

@@

	\begin{section}{Backscatter Detection and Achievable Rates}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems. In the primary downlink system, the AP transmits information to the single-antenna user. In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader. Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging. One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

@@

			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$. For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

@@

			Consider the Maximum-Likelihood (ML) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			the corresponding decision rule is
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{ML}},
				\label{eq:decision_rule}
			\end{equation}
			and the detection threshold is
			\begin{equation}
				T_{i,{i'}}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
				\label{eq:detection_threshold}
			\end{equation}

@@

			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, with the CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Sum backscatter rate}
			We first introduce some prerequisites of information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, collect the input probability distribution of all tags at all states into $\mathcal{P} \triangleq \{P_k(\bar{c}_{m_k}) : m_k \in \mathcal{M}, k \in \mathcal{K}\}$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
				\label{eq:information_function}
			\end{equation}
			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is defined as
			\begin{equation}
				I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),
				\label{eq:marginal_information_function}
			\end{equation}
			and the mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{align}
				I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right]\label{eq:mutual_information}\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}
			\end{align}

			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I_{\mathrm{B}}(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $\mathcal{P}$.\footnote{Note that the contribution of the precoder and detection threshold are modelled within the discrete memoryless MAC.}
		\end{subsection}

		\begin{subsection}{Ergodic primary rate}
			Once the tag input combination is successfully decoded, the user can eliminate backscatter uncertainty and model its contribution within the equivalent primary channel \eqref{eq:equivalent_primary_channel}. As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. Hence, the ergodic primary rate can be expressed as \footnote{The unit of \eqref{eq:backscatter_sum_rate} is \gls{bpcu} while the unit of \eqref{eq:primary_ergodic_rate} is \gls{bpsphz}.}
			\begin{align}
				I_{\mathrm{P}}
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
				\label{eq:primary_ergodic_rate}
			\end{align}
			which is also a function of the tag input distribution $\mathcal{P}$.
			% $P(c_{\mathcal{K}})$.
		\end{subsection}
	\end{section}

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary-backscatter rate region}
			Define the weighted sum primary-backscatter rate as
			\begin{equation}
				I \triangleq \rho I_{\mathrm{B}}(c_{\mathcal{K}} ; z) + (1 - \rho) I_{\mathrm{P}},
			\end{equation}
			where $\rho \in [0,1]$ denotes the priority of the primary link. To investigate how the primary and backscatter links influence each other, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum rate subject to the average transmit power and input probability constraints

			\begin{maxi!}
				{\scriptstyle{\mathcal{P},\mathcal{T},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
			\end{maxi!}

			As problem \eqref{op:rate_region} is not jointly convex over $\mathcal{P}$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose a Block Coordinate Descent (BCD) method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\mathcal{T}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless MAC can be determined by \eqref{eq:mac}, and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\mathcal{P}}}{I}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless MAC (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless MAC, the capacity can be achieved by an elementary discrete memoryless MAC included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless MACs.}

			% Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity. The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary MAC (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions. Also, the capacity of an arbitrary MAC is achieved by an elementary MAC included within.}
			% We restrict the discussion of this paper to elementary MACs.
